Replication of Gantman et al. 2024

### 2024-03-15 manuscript.qmd
fix wording in fashion popout results

In the fashion condition, there was a significant difference in the ERP for fashion and non-fashion words in the effect in the P3 window ($\beta$ = `r p3_model_fashion_popout_beta %>% round(3)`, *SE* = `r p3_model_fashion_popout_se %>% round(3)`, *z* = `r p3_model_fashion_popout_z %>% round(3)`, *p* = `r p3_model_fashion_popout_p %>% format(scientific=FALSE)`). There was no significant difference in the P2 window, ($\beta$ = `r p2_model_fashion_popout_beta %>% round(3)`, *SE* = `r p2_model_fashion_popout_se %>% round(3)`, *z* = `r p2_model_fashion_popout_z %>% round(3)`, *p* = `r p2_model_fashion_popout_p %>% format(scientific=FALSE)`), N2 window ($\beta$ = `r n2_model_fashion_popout_beta %>% round(3)`, *SE* = `r n2_model_fashion_popout_se %>% round(3)`, *z* = `r n2_model_fashion_popout_z %>% round(3)`, *p* = `r n2_model_fashion_popout_p %>% format(scientific=FALSE)`), and LPP window ($\beta$ = `r lpp_model_fashion_popout_beta %>% round(3)`, *SE* = `r lpp_model_fashion_popout_se %>% round(3)`, *z* = `r lpp_model_fashion_popout_z %>% round(3)`, *p* = `r lpp_model_fashion_popout_p %>% format(scientific=FALSE)`).

>>>>

In the fashion condition, there fashion words elicited a more positive ERP than non-fashion words in the P3 window ($\beta$ = `r p3_model_fashion_popout_beta %>% round(3)`, *SE* = `r p3_model_fashion_popout_se %>% round(3)`, *z* = `r p3_model_fashion_popout_z %>% round(3)`, *p* = `r p3_model_fashion_popout_p %>% format(scientific=FALSE)`). There was no significant difference in the P2 window, ($\beta$ = `r p2_model_fashion_popout_beta %>% round(3)`, *SE* = `r p2_model_fashion_popout_se %>% round(3)`, *z* = `r p2_model_fashion_popout_z %>% round(3)`, *p* = `r p2_model_fashion_popout_p %>% format(scientific=FALSE)`), N2 window ($\beta$ = `r n2_model_fashion_popout_beta %>% round(3)`, *SE* = `r n2_model_fashion_popout_se %>% round(3)`, *z* = `r n2_model_fashion_popout_z %>% round(3)`, *p* = `r n2_model_fashion_popout_p %>% format(scientific=FALSE)`), and LPP window ($\beta$ = `r lpp_model_fashion_popout_beta %>% round(3)`, *SE* = `r lpp_model_fashion_popout_se %>% round(3)`, *z* = `r lpp_model_fashion_popout_z %>% round(3)`, *p* = `r lpp_model_fashion_popout_p %>% format(scientific=FALSE)`).
